Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining

### 2015-09-07 5_results_discussions/coselog-wabo/coselog-wabo.tex
no message

>>>>

In \textit{Environmental Permit Application Process} dataset \cite{coselog-data}, there are total of 1214 cases and 2142 events with a variable distribution between event logs of municipalities and municipalities are used as organizational logs.

\begin{itemize}
  \item In \textit{Process Model Mining} stage, with 10\% of noise threshold, high fitness values are achieved; however, some of the process models like Municipality \#5 and \#4 resulted with low appropriateness values. 
  \item In \textit{Performance Indicator Analysis} stage, after calculating the performance indicators, municipalities are clustered based on these values and three clusters are created, Municipality \#1 is located in the first cluster; Municipality \#2 and \#4 are located in the second cluster; and Municipality \#3 and \#5 are grouped in to the last cluster.
  \item In \textit{Mismatch Pattern Analysis} stage, it can be stated that as the similarity between process models of municipalities increases, number of mismatch patterns decreases on most of the cases. When further analyzed, it can be seen that Municipalities \#4 and \#5, which have significantly more complex process model compared to others, fails in spotting mismatch patterns according to \textit{graph-edit similarity}.
  \item In \textit{Recommendation Generation} stage, an organization and performance difference threshold is selected as analysis input likewise the previous dataset. For different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:coselog-wabo-recommendation-generation-analysis} for the thresholds of 25 \%, 50 \% and 75 \% since these are the breaking points for performance indicator changes. As plotted in Figure~\ref{fig:coselog-wabo-recommendation-generation-analysis-k3}, in addition to Municipality \#1, now Municipality \#3 and \#5 have the learning potential from other clusters. However, Municipality \#2 and \#4 performs better in all performance indicators which yielded no mismatch pattern analysis data for them. Increasing cluster sizes in this analysis shows that organizations can learn more from each other but it has the potential danger of overfitting to other organizations process model. 
	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{5_results_discussions/coselog-wabo/recommendation-generation-analysis-k3}
		\caption{Recommendation Generation analysis for Environmental Permit Application Process dataset (3 Clusters)}
	  \label{fig:coselog-wabo-recommendation-generation-analysis-k3}
	\end{figure}
\end{itemize}

### 2015-09-07 5_results_discussions/loan-application-process/loan-application-process.tex
no message

In \textit{Process Model Mining} stage, process models resulted with perfect fitness and high appropriateness as it is expected from a synthetically generated dataset without noise.

In \textit{Performance Indicator Analysis} stage, firstly event logs are replayed over process models and performance indicators are calculated and then organizations are clustered based on their performance indicators. In order to avoid overfitting,  with two clusters, Variant \#1, \#2, and \#4 are grouped into one cluster where only Variant \#3 is left to other cluster.

In \textit{Mismatch Pattern Analysis} stage, number of mismatch patterns are analyzed with the \textit{graph-edit similarity} between each two organization. As the similarity between process models decreases our method spots more mismatch patterns for most of the variants and it ensures that the developed mismatch pattern analyzers work as expected for this dataset.

In \textit{Recommendation Generation} stage, an organization and performance difference threshold is selected as analysis input. For the selected organization's cluster, all other clusters are checked for performing better than the specified threshold. Instead of all mismatch patterns between organizations, only the mismatch patterns that are potential causes of other organizations to perform better are listed. For different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:loan-recommendation-generation-analysis}. 
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{5_results_discussions/loan-application-process/recommendation-generation-analysis}
	\caption{Recommendation Generation analysis for Loan Application Process dataset}
  \label{fig:loan-recommendation-generation-analysis}
\end{figure}
In order to construct the data in Figure~\ref{fig:loan-recommendation-generation-analysis}, every organization is selected one-by-one with different threshold values. For every analysis, number of performance indicators and average number of mismatch patterns causing them are plotted. In addition, total number of mismatch patterns without clustering for each organization is added to the plot as an upper bound. With the help of this upper bound, responsiveness and degree of helping the user to focus on the performance improvement can be analyzed. As can be seen, for each threshold value, average number of mismatch patterns \textit{with performance indicator clustering} are very low compared to \textit{without clustering}. In other words, when user wants to improve its performance with any threshold, there is significantly less number of mismatch patterns on average to check. This shows the methodology proposed in this thesis can help users to focus on differences between organizations given this dataset.

>>>>

\begin{itemize}
  \item In \textit{Process Model Mining} stage, process models resulted with perfect fitness and high appropriateness as it is expected from a synthetically generated dataset without noise.
  \item In \textit{Performance Indicator Analysis} stage, firstly event logs are replayed over process models and performance indicators are calculated and then organizations are clustered based on their performance indicators. In order to avoid overfitting,  with two clusters, Variant \#1, \#2, and \#4 are grouped into one cluster where only Variant \#3 is left to other cluster. 
  \item In \textit{Mismatch Pattern Analysis} stage, number of mismatch patterns are analyzed with the \textit{graph-edit similarity} between each two organization. As the similarity between process models decreases our method spots more mismatch patterns for most of the variants and it ensures that the developed mismatch pattern analyzers work as expected for this dataset. 
  \item In \textit{Recommendation Generation} stage, an organization and performance difference threshold is selected as analysis input. For the selected organization's cluster, all other clusters are checked for performing better than the specified threshold. Instead of all mismatch patterns between organizations, only the mismatch patterns that are potential causes of other organizations to perform better are listed. For different threshold values, number of performance indicators that are performing better for the selected organization and spotted mismatch patterns are plotted in Figure~\ref{fig:loan-recommendation-generation-analysis}. 
    \begin{figure}
    	\centering
    	\includegraphics[width=\textwidth]{5_results_discussions/loan-application-process/recommendation-generation-analysis}
    	\caption{Recommendation Generation analysis for Loan Application Process dataset}
      \label{fig:loan-recommendation-generation-analysis}
    \end{figure}
  In order to construct the data in Figure~\ref{fig:loan-recommendation-generation-analysis}, every organization is selected one-by-one with different threshold values. For every analysis, number of performance indicators and average number of mismatch patterns causing them are plotted. In addition, total number of mismatch patterns without clustering for each organization is added to the plot as an upper bound. With the help of this upper bound, responsiveness and degree of helping the user to focus on the performance improvement can be analyzed. As can be seen, for each threshold value, average number of mismatch patterns \textit{with performance indicator clustering} are very low compared to \textit{without clustering}. In other words, when user wants to improve its performance with any threshold, there is significantly less number of mismatch patterns on average to check. This shows the methodology proposed in this thesis can help users to focus on differences between organizations given this dataset.
\end{itemize}
